\Huge Conferences in an Era of Expensive Carbon

### 2019-06-20 main.tex
Better version of the alternative origin chart
Switched to using sigplan-confs2
Added distances chart

\begin{figure}[t]
\centering
\includegraphics[width=6in]{SIGPLAN-confs.png}
\includegraphics[width=6in]{ParticipantsOriginAll.png}
\caption{Top: carbon footprint per participant for travel to recent SIGPLAN
  conferences\iflater\bcp{Get better file from the other paper, or get
    better version of this one from Crista.}\fi.  Bottom: Origin of
  participants for each conference.  \bcp{Explain in more detail, once we
    have Crista's new figures.}} 
\label{fig:confs}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=6in]{SIGPLAN-confs2.png}
\includegraphics[width=6in]{ParticipantsOriginAll2.png}
\includegraphics[width=6in]{Distances.png}
\caption{Top: carbon footprint per participant for travel to recent SIGPLAN
  conferences\iflater\bcp{Get better file from the other paper, or get
    better version of this one from Crista.}\fi.  Middle: Origin of
  participants for each conference. \bcp{Explain in more detail, once we
    have Crista's new figures.} Bottom: Distances traveled by participants, one way, in Km; middle dashed line is the median travel distance.}
\label{fig:confs}
\end{figure}
